Final Reports with a Main Body of more than 40 pages can only be submitted with prior approval of the team’s Academic Supervisor and Academic Examiner.  Otherwise, a significant poor-presentation penalty may be applied by one or both assessing academics.

Introduction section begins the story of your project.  Include a clear statement of objectives and the scope of the project (the Scope of Works document can be used as a basis).

The main activities of the client organization (if applicable) can be introduced.

Your report can then begin with the starting point of the project – the “need” or “want”. \\

-\\

This project is titled ``Hybrid UAV Development for Emergency Response'', it is a sub-division project of Melbourne Autonomous Search and Rescue (MASR). MASR is the official entrant into the UAV  Challenge - Medical Express 2016.\\

The UAV project entails the design and development of a fully custom UAV which is able to autonomously survey an area and perform search and rescue actions. Specifically, Team CP-CBU-155 was responsible for the development of mechanical design, flight controls, autonomous software, novel sensing method, integration as well as operational roles of developed UAVs.\\

The primary objectives of the project were the following:

\begin{enumerate}
	\item Develop a UAV system to meet challenge requirements
	\item Achieve a functional UAV (that is to be continued on by next years team)
	\item Introduce design novelty \\
\end{enumerate}

A successful UAV capable of search and rescue applications will incorporate the following features:
\begin{itemize}
	\item Payload receipt and transportation
	\item Automated target identification with the ability to communicate subsequent geo-tagging
	\item Capacity to switch between Vertical Take Off and Landing (VTOL) and traditional fixed-wing flight modes
	\item Capacity to switch between automated and manual flight modes through user commands
	\item A total flight travel distance of at least 60km
	\item A total flight duration of at least 60 minutes\\
\end{itemize}

This years team was tasked to 

This project will incorporate the
